Identifying regime transitions for water governance at a basin scale

### 2023-05-31 paper/diff/v-8.2.2.tex
docs(paper): :memo: 更新开放数据声明

\section*{Open Research Section}
Data deposition: All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events have been deposited at \url{https://doi.org/10.5281/zenodo.7955501}~\cite{shuang_song_2023_7955501}.

@@

\bibliography{../v-8.2.1.bib}

>>>>

\section*{Open Research Section}
Data deposition: All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events have been deposited at \url{https://doi.org/10.5281/zenodo.7955500}~\cite{shuang_song_2023_7955500}.

@@

\bibliography{../mybibtex.bib}

### 2023-05-31 paper/diff/v-8.2.3.tex
docs(paper): :memo: 更新开放数据声明

\section*{Open Research Section}
Data deposition: All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events have been deposited at \url{https://doi.org/10.5281/zenodo.7955500}~\cite{shuang_song_2023_7955500}.

@@

\bibliography{../mybibtex.bib}

>>>>

\section*{Open Research Section}
All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events are available under CC-BY 4.0 license~\cite{shuang_song_2023_7955500}.
Figures were made with Matplotlib version 3.7.1~\cite{Hunter:2007} and python-ternary version 1.0.8~\cite{pythonternary}.
These open sourced softwares are available under the Matplotlib license at \url{https://github.com/matplotlib/matplotlib} and the MIT license at \url{https://github.com/marcharper/python-ternary}, separately.

@@

\bibliography{
../mybibtex.bib,
../others.bib
}

### 2023-05-31 paper/main/manuscript.tex
docs(paper): :memo: 更新开放数据声明

\section*{Open Research Section}
All the used datasets and their links are detailed described in the Section~\ref{sec:datasets}.
% The National Long-term Water Use Dataset of China (NLWUD) dataset within the Yellow River Basin uploaded.

>>>>

\section*{Open Research Section}
All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events are available under CC-BY 4.0 license~\cite{shuang_song_2023_7955500}.
Figures were made with Matplotlib version 3.7.1~\cite{Hunter:2007} and python-ternary version 1.0.8~\cite{pythonternary}.
These open sourced softwares are available under the Matplotlib license at \url{https://github.com/matplotlib/matplotlib} and the MIT license at \url{https://github.com/marcharper/python-ternary}, separately.
